\subsection{Author Contributions}
\label{subsec:contribution}

\subsubsection{Luca Vendruscolo}

\begin{itemize}
    \item \textbf{Joint angle detection}: Implemented the YOLOv8 pose estimation model to get joint angles.
    \item \textbf{Data collection}: Made a portable Raspberry Pi setup with a gyroscope sensor to get training data.
    \item \textbf{Model training}: Trained a ConvNeXt model to find the angle of the bike.
    \item \textbf{Web application}: Created the inital framework for the website's front and back ends.
    \item \textbf{Video processing}: Added serverless GPU processing to the backend for the website.
    \item \textbf{Documentation}: Helped with writing documentation.
\end{itemize}

%This is an inital draft 

\subsubsection{Kyle Fram}

\begin{itemize}
    \item \textbf{Data collection}: Helped get data for the bike angle model.
    \item \textbf{Pose estimation improvements}: Added ankle angle estimation.
    \item \textbf{Domain knowledge}: Looked at cycling biomechanics research to suggest adjustments to the bike.
    \item \textbf{Documentation}: Helped with writing documentation.
\end{itemize}

\subsubsection{Fivos Papanikolaou}

\begin{itemize}
    \item \textbf{Data collection}: Helped get data for the bike angle model.
    \item \textbf{Bayesian optimisation}: Implemented Bayesian optimisation for estimating angles.
    \item \textbf{Fit recommendations}: Used angles from the models to create the recommendation logic.
    \item \textbf{Documentation}: Helped with writing documentation.
\end{itemize}

\subsection{Experimentation}

\paragraph{EMPTY} 
\begin{enumerate}
    \item 
\end{enumerate}
